Clustering Beat-Chroma Patterns in a Large Music Database

### 2010-03-23 Paper/Paper.tex
fixed comment about code 8

The 25 most frequently used codewords in the testing set are shown in
Figure \ref{fig:codes1}.  The codewords primarily consist of sustained
notes and simple chords.  Since they are designed to be key-invariant,
specific notes do not appear.  Instead the first 7 codewords
correspond to a single note sustained across two bars (codeword 1),
perfect fifth (codes 2 and 3) and fourth intervals (codes 4 7), and a
major and minor triads (code 6 and 5).  Many of the remaining
codewords correspond to transitions from one chord to another, \eg a
transition from a major triad to a minor triad in code 8.

>>>>

The 25 most frequently used codewords in the testing set are shown in
Figure \ref{fig:codes1}.  The codewords primarily consist of sustained
notes and simple chords.  Since they are designed to be key-invariant,
specific notes do not appear.  Instead the first 7 codewords
correspond to a single note sustained across two bars (codeword 1),
perfect fifth (codes 2 and 3) and fourth intervals (codes 4 7), and a
major and minor triads (code 6 and 5).  Many of the remaining
codewords correspond to transitions from one chord to another, \eg a
transition from one major triad to another (\ie Cmaj to Fmaj assuming
that chroma 0 is C) in code 8.  Does this transition have a better
name like ``relative x''?
